### 2016-03-02 ch02-qlogms/excitation-design.tex
Guidelines improved

  The arguments for a logarithmically spaced grid with an infinite span remain approximately valid for quasi-logarithmically spaced grids with a finite frequency support if the resonance peak of the system under test lies well within the `bulk' of the frequency grid with finite support, i.e. $\RightOpenInterval{\frac{2\pi \Delta f}{\alpha - 1}, +\infty}$.
  In particular for lightly-damped sub-systems, $\wdB \approx \ClosedInterval{(1-\damping)\wn, (1+\damping)\wn}$, such that the resonance peak is in the bulk of the frequency grid when
  \begin{equation} 
    \frac{2 \pi \Delta f}{alpha -1} \leq \left( 1 - \damping \right) \wn
    \text{.}
    \label{eq:excitation:systemInBulk:generic}
  \end{equation}
  For more reliable results, however, it is adviced to also have a few logarithmically spaced frequency lines, outside of the resonance peak of the actual system for a more robust result.
  In practice, this means that systems with their resonance peak at the lowest and the very highest edge of the frequency band may not be observed with identical quality as systems at intermediate frequencies.

@@

>>>>

  The arguments for a logarithmically spaced grid with an infinite span remain approximately valid for quasi-logarithmically spaced grids with a finite frequency support if the resonance peak of the system under test lies well within the `bulk' of the frequency grid with finite support, i.e. $\RightOpenInterval{\frac{2\pi \Delta f}{\alpha - 1}, +\infty}$.
  In particular for lightly-damped sub-systems, $\wdB \approx \ClosedInterval{(1-\damping)\wn, (1+\damping)\wn}$, such that the resonance peak is in the bulk of the frequency grid when
  \begin{equation} 
    \frac{2 \pi \Delta f}{\alpha -1} \leq \left( 1 - \damping \right) \wn
    \text{.}
    \label{eq:excitation:systemInBulk:generic}
  \end{equation}
  For more reliable results, however, it is adviced to also have a few logarithmically spaced frequency lines, outside of the resonance peak of the actual system for a more robust result.
  In practice, this means that systems with their resonance peak at the lowest and the very highest edge of the frequency band may not be observed with identical quality as systems at intermediate frequencies.

@@

\begin{guideline}[Use quasi-logarithmic multisines as initial excitation]
  Quasi-logarithmic multisines with pink-colored amplitude spectrum facilitate the measurement of many sharp resonance peaks over a wide frequency band of interest with a constant quality.
\end{guideline}

\begin{guideline}[Design the logarithmic grid for the damping of the system: $\alpha \leq  1 + \xi_{\min}$]
   To measure a resonant system with damping $\damping > \damping[\min]$ well, a (pink) quasi-logarithmic multisine with frequency ratio $\frac{\omega_k}{\omega_{k-1}} \leq \alpha \leq 1 + \damping[\min]$ is recommended.
   Smaller frequency ratios provide more measurement points at the cost of a reduced \gls{SNR} per frequency bin.
   As such, $\alpha = 1 + \damping$ provides a nice trade-off: it has the required resolution and the best \gls{SNR} per bin.
\end{guideline}

\begin{guideline}[Ensure $\Delta \omega < (\damping - \damping^2) \wn \approx \damping \wn$]
 A quasi-logarithmic multisine with frequency resolution $\Delta \omega$ and tuned frequency spacing $\alpha$ is only guaranteed to properly excite resonances
\end{guideline}

### 2016-03-02 ch05-initvals/initial-values.tex
Vuistregels etc.
Guidelines improved

\begin{algorithm}
\caption{Levenberg-Marquardt~\citep{Marquardt1963}, \citep[Sec. 9.L.4]{Pintelon2012}}\label{LMalgo}
\begin{algorithmic}[1]
  \Require Cost function \eqref{eq:MLEcf} is rewritten as $V(\theta) = \epsilon(\theta)^{\TT} \epsilon(\theta)$. 
\Function{LevenbergMarquardt}{$\epsilon(\theta),  \theta^{\mathrm{init}}$}
   \State $\atIter[0]{\theta} \gets \theta^{\mathrm{init}}$
   \Comment{$\atIter[i]{X}$ denotes $X$ at iteration $i$.}
   \For{$i$ \textbf{in} $1 \to \infty$}
      \State $U \, \Sigma \, W^{\TT} \gets \code{svd}\left( \frac{\partial \epsilon(\atIter[i-1]{\theta})}{\partial \theta}\right)$ 
        \Comment{Singular value decomposition of Jacobian}
      % \State $
      %                  \text{Denote }\Sigma \equiv 
      %                  \left[ \begin{matrix} 
      %                  \sigma_1         & \deemph{0} & \deemph{\cdots} &           & \deemph{0}      \\
      %                  \deemph{0}      & \sigma_2    &                   &           &                   \\
      %                  \deemph{\vdots} &              & \ddots            &           & \deemph{\vdots} \\
      %                                    &              &                   & \sigma_n &                   \\
      %                   \deemph{0}      &              & \deemph{\cdots} &           & \deemph{0}      
      %                   \end{matrix}\right]
      %                $
      % \State \textbf{if} $i=1$ \textbf{ then} $\lambda \gets \max(\sigma) / 100$
      \If{$\lambda$ is undefined}
        \State $\lambda \gets \max(\Set{\Sigma_{11}, \ldots, \Sigma_{nn}})/100$
      \EndIf
      \State $\Sigma_{kk} \gets \frac{\Sigma_{kk}}{(\Sigma_{kk}^2 + \lambda^2)} \quad \forall k \in \Set{1, \ldots, n}$
      \State $\delta\theta \gets - W  \Sigma^{\TT}  U^{\TT} \epsilon(\atIter[i-1]{\theta})$
      \State $\atIter[i]{\theta} \gets \frac{(\atIter[i-1]{\theta} + \delta\theta) }{ \norm[2]{\atIter[i-1]{\theta} + \delta\theta} }$
      \If{$V(\atIter[i]{\theta}) > V(\atIter[i-1]{\theta})$} \Comment{Current step is a deterioration}
         \State $\atIter[i]{\theta} \gets \atIter[i-1]{\theta}$ \Comment{Restart loop from previous estimate}
          \State $\lambda \gets 10 \lambda$ 
      \Else
          \State $\lambda \gets 0.4 \lambda$
      \EndIf
      \If {$\norm[2]{\delta\theta} < n_{\theta}  \cdot 10^{-6} \norm[2]{\atIter[i]{\theta}}$}
          \State \textbf{return} $\hat{\theta} \gets \atIter[i]{\theta}$
      \EndIf
   \EndFor
\EndFunction
\end{algorithmic}
\end{algorithm}

@@

>>>>

\begin{algorithm}
\caption{Levenberg-Marquardt~\citep{Marquardt1963}, \citep[Sec. 9.L.4]{Pintelon2012}}\label{LMalgo}
\begin{algorithmic}[1]
  \Require Cost function \eqref{eq:MLEcf} is rewritten as $V(\theta) = \InnerProductSelf{\epsilon(\theta)}$. 
\Function{LevenbergMarquardt}{$\epsilon(\theta),  \theta^{\mathrm{init}}$}
   \State $\atIter[0]{\theta} \gets \theta^{\mathrm{init}}$
   \Comment{$\atIter[i]{X}$ denotes $X$ at iteration $i$.}
   \For{$i$ \textbf{in} $1 \to \infty$}
      \State $U \, \Sigma \, W^{\TT} \gets \code{svd}\left( \frac{\partial \epsilon(\atIter[i-1]{\theta})}{\partial \theta}\right)$ 
        \Comment{Singular value decomposition of Jacobian}
      % \State $
      %                  \text{Denote }\Sigma \equiv 
      %                  \left[ \begin{matrix} 
      %                  \sigma_1         & \deemph{0} & \deemph{\cdots} &           & \deemph{0}      \\
      %                  \deemph{0}      & \sigma_2    &                   &           &                   \\
      %                  \deemph{\vdots} &              & \ddots            &           & \deemph{\vdots} \\
      %                                    &              &                   & \sigma_n &                   \\
      %                   \deemph{0}      &              & \deemph{\cdots} &           & \deemph{0}      
      %                   \end{matrix}\right]
      %                $
      % \State \textbf{if} $i=1$ \textbf{ then} $\lambda \gets \max(\sigma) / 100$
      \If{$\lambda$ is undefined}
        \State $\lambda \gets \max(\Set{\Sigma_{11}, \ldots, \Sigma_{nn}})/100$
      \EndIf
      \State $\Sigma_{kk} \gets \frac{\Sigma_{kk}}{(\Sigma_{kk}^2 + \lambda^2)} \quad \forall k \in \Set{1, \ldots, n}$
      \State $\delta\theta \gets - W  \Sigma^{\TT}  U^{\TT} \epsilon(\atIter[i-1]{\theta})$
      \State $\atIter[i]{\theta} \gets \frac{(\atIter[i-1]{\theta} + \delta\theta) }{ \norm[2]{\atIter[i-1]{\theta} + \delta\theta} }$
      \If{$V(\atIter[i]{\theta}) > V(\atIter[i-1]{\theta})$} \Comment{Current step is a deterioration}
         \State $\atIter[i]{\theta} \gets \atIter[i-1]{\theta}$ \Comment{Restart loop from previous estimate}
          \State $\lambda \gets 10 \lambda$ 
      \Else
          \State $\lambda \gets 0.4 \lambda$
      \EndIf
      \If {$\norm[2]{\delta\theta} < n_{\theta}  \cdot 10^{-6} \norm[2]{\atIter[i]{\theta}}$}
          \State \textbf{return} $\hat{\theta} \gets \atIter[i]{\theta}$
      \EndIf
   \EndFor
\EndFunction
\end{algorithmic}
\end{algorithm}

@@

\begin{guideline}[Try regularization to improve convergence]
\label{guide:initvals:try-regularization}
Regularized estimators, such as \gls{RFIR}, sometimes provide better estimates than the `true' model parameters.
\end{guideline}

\begin{guideline}[Try different initial values for non-convex optimization]
\label{guide:initvals:try-many-initial-values}
Trying different initial values is quite inexpensive, but the quality of the final model may improve by several order of magnitude if a local minimum can be avoided.
As such, using multiple initial values, especially ones that have been derived with good judgment, pays off.
\end{guideline}
